\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}

\usepackage{fancyhdr}
\setlength{\headheight}{16pt}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.2pt} % no line in header area
\fancyhead{}
\pagestyle{fancy}
\fancyhf{}
\lhead{Computational Aspects of Digital Fabrication}
\rhead{Jan Pokorný}
\rfoot{\thepage}
\title{Dosimeter game}
\begin{document}
\vspace*{10px}
{\huge{Dosimeter game: Info sheet}}

\section{Game}
The goal of the game is to survive and find a NFC tag. 
The player gathers information about its surrounding through a device.
The device gives the player a rough distance from the goal item and a strength of the radiation.
If the player is area with radiation, he loses health points.
If the health points of the player ever reaches a zero, the game is over.

\subsection{Controls}
\begin{enumerate}
\item Use the NFC card to restart the device by putting it next to the NFC reader (slightly darker rectangle, left of the button).
\item Press the button to change the displayed information. THe display displays these types of information:
\begin{itemize}
\item Goal(G): The distance (not in meters - signal strength from the ) from the goal.
\item Time: Time since the beggining of the game.
\item Radiation(r): Amount of radiation the player is receiving. The higher the radiation, the faster loses the player health points. 
\item Health(H): Number of health points remaining, if this counter reaches zero, the game ends.
The letter in parenthesis is displayed as the first character on the display.
\end{itemize}
\item Monitor the health bar, the less LEDs are lit up, the lower the amount of health points the player has.
\item Find the NFC tag and put it next to the NFC reader. The display now shows how fast you were.
\item Write your time to the scoreboard.
\end{enumerate}

\section{How to make}
\subsection{Components}
The main components are:
\begin{itemize}
    \item RaspberryPi 4 B
    \item 4 Digit Display V1.2 (HW-069) 
    \item RFID-RC522
    \item Powerbank
\end{itemize}
Furthemore, standard components for RPi as LEDs, button, cables were used.

\subsection{PIN layout}
\begin{itemize}
    \item Digit Display V1.2 (HW-069)
        \begin{itemize}
            \item CLK - GPIO 3 (5)
            \item DIO - GPIO 2 (3)
            \item VCC - 3.3V (1)
            \item GND - GND(6)
        \end{itemize}
    \item RFID-RC522
        \begin{itemize}
            \item SDA - GPIO 8 (24)
            \item SCK - GPIO 11 (23)
            \item MOSI - GPIO 10 (19)
            \item MISO - GPIO 9 (21)
            \item IRQ - Not used
            \item GND - GND (20)
            \item RST - GPIO 25 (22)
            \item 3.3V - 3.3V (17)
        \end{itemize}
    \item Button
        \begin{itemize}
            \item Power - 5V (4)
            \item Detect - GPIO 4 (7)
        \end{itemize}
    \item LEDS
        \begin{itemize}
            \item L1 - GPIO 5 (29)
            \item L2 - GPIO 6 (31)
            \item L3 - GPIO 13 (33)
            \item L4 - GPIO 19 (35)
            \item L5 - GPIO 26 (37)
            \item L6 - GPIO 20 (38)
            \item Status - GPIO 21 (40)
            \item GND - GND (39)
        \end{itemize}
\end{itemize}
\subsection{Tutorial}

\subsection{}
\end{document}
